\documentclass[a4paper]{exam}

\usepackage{amsmath,amssymb, amsthm}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{titling}



% Header and footer.
\pagestyle{headandfoot}
\runningheadrule
\runningfootrule
\runningheader{CS/MATH 113, SPRING 2026}{Pset 04: Inference}{\theauthor}
\runningfooter{}{Page \thepage\ of \numpages}{}
\firstpageheader{}{}{}

% \printanswers %Uncomment this line

\title{Problem Set 04: Inference}
\author{Blingblong} % <=== replace with your student ID, e.g. xy012345
\date{CS/MATH 113 Discrete Mathematics\\Habib University\\Spring 2026}

% \qformat{\large\bf \thequestion.}
\qformat{{\large\bf \thequestion. \thequestiontitle}\hfill}
\boxedpoints

\begin{document}
\maketitle

\begin{questions}
    \titledquestion{Basic rules of inference}
    Given that the following statements are true
    \begin{itemize}
        \item $p \implies q$
        \item $s \land \neg p \implies \neg r$
        \item $V \implies \neg q$
        \item $(t \lor s) \land (\neg t \lor \neg U)$
        \item $U \implies V$
        \item $U$
    \end{itemize}
    Show that $\neg r$ is true.
    \begin{solution}
        % Enter solution here.
    \end{solution}


    \titledquestion{1999 bizarre summer}
    In a crazy noisy bizarre town Morioh there is a serial killer on the loose who is weirdly obsessed with hands. You have to help Josuke and the gang to find the serial killer. So far you have been able to gather the following clues:
    \begin{itemize}
        \item If the killer is at Chef Tonio's restaurant then the killer has the stand Highway Star.
        \item The killer's stand is not Sheer Heart Attack or the killer doesn't works at Café Rengatei.
        \item If the killer wants to live quietly then the killer works at Kame Yu department store.
        \item The killer works at Café Rengatei or the killer doesn't have the stand Highway Star.
        \item If the killer isn't at Chef Tonio's restaurant then the killer wants to live quitely.
        \item The killer's stand is Sheer Heart Attack or has the stand Red Hot Chili Pepper.
        \item If the killer works at Café Rengatei then the killer has the stand Super Fly.
        \item The killer's stand is not Red Hot Chili Pepper.
        \item If the killer has the stand Super Fly and the wants to live quietly then the killer is Toyohiro Kanedaichi.
        \item If the killer works at Kame Yu department store and has the stand Sheer Heart Attack or has the stand Killer Queen then the killer is Yoshikage Kira.
        \item If the killer has the stand Red Hot Chili Pepper or the killer doesn't want to live quietly then the killer is Akira Otoishi. 
        \item If the killer has the stand Highway Star then the killer is Yuya Fungami.
    \end{itemize}
    Using the above clues determine who is the killer by referring to the relevant rule of inference at each step of your argument.
    \begin{solution}
        % Enter solution here
    \end{solution}


    \titledquestion{Elementary my dear Watson}
    Following is a quote by Sherlock Holmes from \textit{“A Study in Scarlet”} in which he solves a murder case.
    \begin{quote}
    ``And now we come to the great question as to the reason why. Robbery has not been the object of the murder, for nothing was taken. Was it politics, then, or was it a woman? That is the question which confronted me. I was inclined from the first to the latter supposition. Political assassins are only too glad to do their work and fly. This murder had, on the contrary, been done most deliberately, and the perpetrator has left his tracks all over the room, showing he had been there all the time.''
    \end{quote}
    After stating the above, Sherlock Holmes concludes: \textit{``It was a woman''}.

    Show the premises and logical inferences involved in deducing the conclusion.

    \begin{solution}
        % Enter solution here
    \end{solution}

    \titledquestion{Rules of inference for quantified}
    \begin{parts}
        \part Show that if $\forall x(P(x) \implies (Q(x) \land S(x)))$ and $\forall x(P(x) \land R(x))$ are true, then $\forall x(R(x) \land S(x))$ is true.
        \begin{solution}
            % Enter solution here
        \end{solution}

        \part Show that if $\forall x(P(x) \lor Q(x))$, $\forall x(\neg Q(x) \lor S(x))$, $\forall x(R(x) \implies \neg S(x))$, and $\exists x\neg P(x)$ are true, then $\exists x\neg R(x)$ is true.
        \begin{solution}
            % Enter solution here
        \end{solution}

    \end{parts}



    \titledquestion{Nihari reasoning}
    \begin{quote}
        ``If this statement is true then Mujtaba is coolest most amazing person with infinite aura and is the best RA.''
    \end{quote}
    What can you infer from this statement? Is Mujtaba the best RA? In propositional logic the above statement can be written as:
     
    $P: P \implies Q$ where $Q:$ ``Mujtaba is coolest most amazing person with infinite aura and is the best RA''. 
    
    Apply rules of inference to reach a conclusion about the truth value of the consequent ($Q$) in the above statement. 
    What if the consequent ($Q$) in the above implication was something absurd such as ``0 = 1''. Would the reasoning still remain valid or is there a flaw in the reasoning? 
    \begin{solution}
        % Enter solution here
    \end{solution} 

    
      
\end{questions}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
